% -*- latex -*-

% This document uses the currvita environment.  For documentation, run
% latex on currvita.dtx (located in texmf/source/latex/currvita in MikTex)
% and view the resulting dvi.

\documentclass{article}

\usepackage[TextAligned]{currvita}
\usepackage{url}

% Resize the paper for smaller margins
\usepackage{geometry}
\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}

\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}

\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}

\cvplace{Sandia National Laboratories}

%TIMESTAMP=`%B %e, %Y'
\date{August 31, 2020}

\sloppy

\begin{document}

  \begin{cv}{Curriculum Vitae}
    \setlength{\cvlabelwidth}{.25in}
    \renewcommand*{\cvlabelfont}{\textsf}

    \begin{cvlist}{Personal Information}
      \item Kenneth Dean Moreland \\
        P.O. Box 5800  MS 1326 \\
        Albuquerque, NM  87185-1326
      \item Telephone: (505) 844-8919 \\
        Email: kmorel@sandia.gov \\
        Web: \url{http://kennethmoreland.com/}
    \end{cvlist}

    \begin{cvlist}{Education}
      \item[Doctor of Philosophy] Computer Science, University of New
        Mexico, Albuquerque, NM, July 2004.
      \item[Master of Science] Computer Science, University of New Mexico,
        Albuquerque, NM, May 2000.
      \item[Bachelor of Science] Computer Science, New Mexico Institute of
        Mining and Technology, Socorro, NM, May 1997.
      \item[Bachelor of Science] Electrical Engineering, New Mexico
        Institute of Mining and Technology, Socorro, NM, May 1997.
    \end{cvlist}

    \begin{cvlist}{Work Experience}
    \item[Sandia National Laboratories (Albuquerque, NM)]\hfill\\
      2013-- Principal Member of Technical Staff, Scalable Analysis and Visualization\\
      2004--2013 Senior Member of Technical Staff, Scalable Analysis and Visualization\\
      2000-2003 Member of Technical Staff, Data Analysis and Visualization\\
      1999-2000 Member of Technical Staff, Distributed Systems Research\\
      1997-1999 Limited Term Employee, Computer Applications for Manufacturing\\
      1995-1997 Student Intern, Mechanical Process Engineering\\
    \end{cvlist}

    % Note: Funding for PI for total of project (where applicable) whereas
    % co-PI just reports funding for our institution.

    \begin{cvlist}{Research Experience (Professional)}
    \item[ECP/VTK-m]\hfill 2017--Present\\
      Updating scientific visualization algorithms in the VTK-m framework for efficient visualization on multi- and many-core processor devices.\\
      DOE Office of Science Exascale Computing Project\\
      Role: PI\\
      Total funding: \$9.7M %(\$4.3M FY17-FY19, \$5.4M FY20-FY23)
    \item[ATDM Scalable Visualization]\hfill 2016--Present\\
      Visualization support for mission-specific science applications for the Advanced Technology Development and Mitigation (ATDM) program.\\
      DOE NNSA ASC Program\\
      Role: PI\\
      Funding: \$800K/year
    \item[XVis: Visualization for the Extreme-Scale Scientific-Computation Ecosystem]\hfill 2014--2017\\
      Providing the foundational research for visualization software for scientific discovery with exascale computing. This work was foundational to start software projects like \mbox{VTK-m} and provide improvements to in situ libraries like Catalyst.
      DOE Office of Science ASCR Program\\
      Role: PI \\
      Total funding: \$4M
    \item[SciDAC Scalable Data Analysis and Visualization Institute]\hfill 2013--2017\\
      Provide technical solutions in the data management, analysis, and
      visualization regimes that are broadly applicable in the
      computational science community for the DOE Office of Science SciDAC program.\\
      DOE Office of Science SciDAC Program\\
      Role: Co-PI\\
      Funding: \$875K
    \item[Data Analysis at Extreme (Dax)]\hfill 2010--2014\\
      Creating a framework for visualization on exascale processors. Dax was one of the precursors to \mbox{VTK-m}.\\
      DOE Office of Science ASCR Program\\
      Role: PI\\
      Total Funding: \$1.5M
    \item[SciDAC Institute for Ultrascale Visualization]\hfill 2006--2012\\
      Addressed visualization challenges for the DOE Scientific Discovery through Advanced Computing effort.
      DOE Office of Science SciDAC Program\\
      Role: Co-PI\\
      Funding: \$900K
    \item[ParaView Development Lead]\hfill 2006--Present\\
      Lead the ASC funded development effort for ParaView, a large-scale
      general visualization solution. Today, ParaView is downloaded hundreds of thousands of times each year.\\
      DOE NNSA ASC Program\\
      Role: PI\\
      Funding: \$1.6M/year % Taken from 7656/08.01 support budget for 2020
    %% \item[Scalable Visualization]\hfill 8/99--Present \\
    %%   Researched, developed, and deployed visualization algorithms designed
    %%   for scalability in parallel environments.
    \item[Massive Graph Visualization]\hfill 2005--2007 \\
      Explored techniques for visualizing providing information in large
      graph structures.\\
      Sandia Laboratories LDRD Program\\
      Role: PI\\
      Funding: \$1.4M
    %% \item[Volume Rendering] Sandia National Laboratories, 8/03--8/07 \\
    %%   Researched and developed unstructured grid volume rendering codes for
    %%   rendering more accurate images in less time.  This includes utilizing
    %%   both CPU and GPU processors as well as employing parallel algorithms.
    \item[Scalable Rendering]\hfill 1999--2005 \\
      Researched and developed parallel rendering codes targeted at performing scientific visualization on cluster computers.  Software targeted for very large inputs and/or to very large displays.\\
      DOE NNSA ASC Program\\
      Role: Key personnel
    \item[Product Realization Environment]\hfill 1996--1999 \\
      Developed and deployed a CORBA-based middleware tool for distributing
      and connecting scientific modeling and simulation codes.\\
      DOE NNSA ASC Program\\
      Role: Key personnel
    \end{cvlist}

    \begin{cvlist}{Research Experience (Academic)}
    \item[Doctoral Research]\hfill University of New Mexico, 8/01--8/04 \\
      Conceived novel mathematical analysis to direct volume rendering
      light transport equation that enables real time display of highly
      accurate, linearly interpolated unstructured volumes.
    \end{cvlist}

    \begin{cvlist}{Publications}
    \item[XVis: Visualization for the Extreme-Scale Scientific Computation]~\\ Ecosystem, Final Report.
      Kenneth Moreland, David Pugmire, David Rogers, Hank Childs, Kwan-Liu Ma, and Berk Geveci.
      Technical Report SAND 2019-9297, Sandia National Laboratories.
      August 2019.
    \item[Efficient Point Merging Using Data Parallel Techniques.]
      Abhishek Yenpure, Hank Childs, and Kenneth Moreland.
      In \emph{Eurographics Symposium on Parallel Graphics and Visualization (EGPGV)}.
      June 2019.
      DOI~10.2312/pgv.20191112.
    \item[In Situ Visualization for Computational Science (Dagstuhl Seminar 18271).]
      Janine C. Bennett, Hank Childs, Christoph Garth, Bernd Hentschel, et al.
      Dagstuhl Reports, pg 1--43.
      2019.
      DOI~10.4230/DagRep.8.7.1.
    \item[Comparing Binary-Swap Algorithms for Odd Factors of Processes.]
      Kenneth Moreland.
      In \emph{Proceedings of the 8th IEEE Symposium on Large Data Analysis and Visualization (LDAV)}.
      October 2018.
      DOI~10.1109/LDAV.2018.8739210.
    \item[The future of scientific workflows.]
      Ewa Deelman, Tom Peterka, Ilkay Altintas, Christopher D Carothers, Kerstin Kleese van Dam, Kenneth Moreland, Manish Parashar, Lavanya Ramakrishnan, Michela Taufer, and Jeffrey Vetter.
      \emph{International Journal of High Performance Computing Applications}, 32(1), January 2018, pg 159--175.
      DOI~10.1177/1094342017704893.
    \item[In Situ Visualization for Computational Science]
      (Dagstuhl Seminar 18271).
      Janine C. Bennett, Hank Childs, Christoph Garth, and Bernd Hentschel.
      Dagstuhl Reports, 2019, pg 1--43. DOI 10.4230/DagRep.8.7.1.
    \item[A Need for Better Management of Heterogenous HPC Resources.]
      Kenneth Moreland and Chuck Atkins.
      Technical Report SAND2018-5743R, Sandia National Laboratories, 2018.
    \item[The future of scientific workflows.]
      Ewa Deelman, Tom Peterka, Ilkay Altintas, Christopher D Carothers, Kerstin Kleese van Dam, Kenneth Moreland, Manish Parashar, Lavanya Ramakrishnan, Michela Taufer, and Jeffrey Vetter.
      \emph{International Journal of High Performance Computing Applications}, 32(1), January 2018, pg 159--175.
      DOI~10.1177/1094342017704893.
    \item[Techniques for Data-Parallel Searching for Duplicate Elements.]
      Brenton Lessley, Kenneth Moreland, Matthew Larsen, and Hank Childs.
      In \emph{IEEE Symposium on Large Data Analysis and Visualization (LDAV)}, October 2017.
      DOI~10.1109/LDAV.2017.8231845.
    \item[Isosurface Visualization Miniapplication.]
      Daniel Bourgeois, Michael Wolf, and Kenneth Moreland.
      In \emph{Center for Computing Research Summer Proceedings 2017}.
      Technical Report SAND2018-2780O, Sandia National Laboratories, 2018, pg 135--142. 
    \item[Optimizing Multi-Image Sort-Last Parallel Rendering.]
      Matthew Larsen, Kenneth Moreland, Chris R. Johnson, and Hank Childs.
      In \emph{IEEE Symposium on Large-Scale Data Analysis and Visualization (LDAV)}, October 2016.
      DOI~10.1109/LDAV.2016.7874308.
    \item[Advanced Scientific Computing Research Exascale Requirements Review.]
      Jeffrey Vetter, Ann Almgren, Phil DeMar, et al.
      September 2016.
      DOI~10.2172/1375638.
    \item[In Situ Methods, Infrastructures, and Applications on High Performance]~\\ Computing Platforms.
      Andrew C. Bauer, Hasan Abbasi, James Ahrens, Hank Childs, Berk Geveci, Scott Klasky, Kenneth Moreland, Patrick O'Leary, Venkatram Vishwanath, Brad Whitlock, and E. Wes Bethel.
      \emph{Computer Graphics Forum}, 32(3), June 2016, pg 577--597.
      DOI~10.1111/cgf.12930.
    \item[VTK-m: Accelerating the Visualization Toolkit for Massively Threaded]~\\ Architectures.
      Kenneth Moreland, Christopher Sewell, William Usher, Li-ta Lo, Jeremy Meredith, David Pugmire, James Kress, Hendrik Schroots, Kwan-Liu Ma, Hank Childs, Matthew Larsen, Chun-Ming Chen, Robert Maynard, and Berk Geveci.
      \emph{IEEE Computer Graphics and Applications}, 36(3), May/June 2016, pg 48--58.
      DOI~10.1109/MCG.2016.48.
    \item[The Tensions of In Situ Visualization.]
      Kenneth Moreland.
      \emph{IEEE Computer Graphics and Applications}, 36(2), March/April, 2016, pg. 5--9.
      DOI~10.1109/MCG.2016.35.
    \item[Why We Use Bad Color Maps and What You Can Do About It.]
      Kenneth Moreland.
      In \emph{Proceedings of Human Vision and Electronic Imaging (HVEI)}, February 2016.
      DOI~10.2352/ISSN.2470-1173.2016.16.HVEI-133.
    \item[ParaView Catalyst: Enabling In Situ Data Analysis and Visualization.]
      Utkarsh Ayachit, Andrew Bauer, Berk Geveci, Patrick O'Leary, Kenneth Moreland, Nathan Fabian, Jeffrey Mauldin.
      In \emph{Proceedings of the First Workshop on In Situ Infrastructures for Enabling Extreme-Scale Analysis and Visualization (ISAV 2015)}, November 2015, pp. 25--29.
      DOI~10.1145/2828612.2828624.
    \item[Formal Metrics for Large-Scale Parallel Performance.]
      Kenneth Moreland and Ron Oldfield.
      In \emph{High Performance Computing}, July 2015.
      DOI~10.1007/978-3-319-20119-1\_34.
    \item[The Future of Scientific]~\\ Workflows: Report of the DOE NGNS/CS Scientific Workflows Workshop.
      Ewa Deelman, Tom Peterka, et al.
      April 2015.
      \url{https://science.energy.gov/~/media/ascr/pdf/programdocuments/docs/workflows_final_report.pdf}.
    \item[Visualization for Exascale: Portable Performance is Critical.]
      Kenneth Moreland, Matthew Larsen, and Hank Childs.
      In \emph{Supercomputing Frontiers and Innovations}, 2(3), 2015.
      DOI~10.14529/jsfi150306.
    \item[Implementing Parallel Algorithms Using the Dax Toolkit.]
      Hendrik Schroots and Kenneth Moreland.
      In \emph{CR Summer Proceedings 2014}, Tech Report SAND 2015-3829 O, December 2014, pg 197--207.
    \item[Finely-Threaded History-Based Topology Computation.] Robert
      Miller, Kenneth Moreland, and Kwan-Liu Ma. In \emph{Eurographics
        Symposium on Parallel Graphics and Visualization}, June 2014. pg.
      41--48. DOI~10.2312/pgv.20141083.
    \item[Evaluation of Methods to Integrate Analysis into a Large-Scale
      Shock] Physics Code. Ron Oldfield, Kenneth Moreland, Nathan Fabian,
      and David Rogers. In \emph{Proceedings of the 28th ACM international
        conference on Supercomputing (ICS'14)}, pg. 83--92, June 2014.
      DOI~10.1145/2597652.2597668.
    \item[A Pervasive Parallel Framework for Visualization: Final Report
      for FWP] 10-014707. Kenneth Moreland. Tech Report SAND 2014-0047,
      Sandia National Laboratories, January 2014.
    \item[A Classification of Scientific Visualization Algorithms for
      Massive] Threading. Kenneth Moreland, Berk Geveci, Kwan-Liu Ma, and
      Robert Maynard. In \emph{Proceedings of the Ultrascale Visualization
        Workshop}, November 2013. DOI~10.1145/2535571.2535591.
    \item[Data Co-Processing for Extreme Scale Analysis Level II ASC
      Milestone] (4745). David Rogers, Kenneth Moreland, Ron Oldfield, and
      Nathan Fabian. Tech Report SAND 2013-1122, Sandia National
      Laboratories, November 2013.
    \item[ADIOS Visualization Schema: A First Step Towards Improving]
      Interdisciplinary Collaboration in High Performance Computing.
      Roselyne Tchoua, Jong Choi, Scott Klasky, Qing Liu, Jeremy Logan,
      Kenneth Moreland, Jingqing Mu, Manish Parashar, Norbert Podhorszki,
      David Pugmire, and Matthew Wolf. \emph{IEEE International Conference
        on eScience}. October 2013, pg. 27--34.
      DOI~10.1109/eScience.2013.24.
    \item[Research Challenges for Visualization Software.] Hank Childs, Berk
      Geveci, Will Schroeder, Jeremy Meredith, Kenneth Moreland,
      Christopher Sewell, Torsten Kuhlen, and E. Wes Bethel. \emph{IEEE
        Computer}, Volume 46, Number 5, May 2013, pg. 34--42.
      DOI~10.1109/MC.2013.179.
    \item[A Survey of Visualization Pipelines.] Kenneth
      Moreland. \emph{IEEE Transactions on Visualization and Computer
        Graphics}, Volume 19, Number 3, March 2013.
      DOI~10.1109/TVCG.2012.133.
    \item[Enabling Production-Quality Scientific-Discovery Tools with Data
      and] Execution Models. Kenneth Moreland, Jeremy Meredith, and Berk
      Geveci. \emph{Tech Report} SAND 2012-10796P, Sandia National
      Laboratories, December 2012.
    \item[Flexible Analysis Software for Emerging Architectures.] Kenneth
      Moreland, Brad King, Robert Maynard, and Kwan-Liu Ma. In
      \emph{Petascale Data Analytics: Challenges and Opportunities
        (PDAC-12)}, November 2012.
    \item[The SDAV Software Frameworks for Visualization and Analysis on]~\\
      Next-Generation Multi-Core and Many-Core Architectures. Christopher
      Sewell, Jeremy Meredith, Kenneth Moreland, Tom Peterka, Dave DeMarle,
      La-ta Lo, James Ahrens, Robert Maynard, and Berk Geveci. In
      \emph{Ultrascale Visualization Workshop}, November 2012.
    \item[Oh, \$\#*@!  Exascale!  The Effect of Emerging Architectures on
      Scientific] Discovery.  Kenneth Moreland.  In \emph{Ultrascale
      Visualization Workshop}, November 2012.
    \item[Redirecting Research in Large-Format Displays for Visualization.]
      Kenneth Moreland. In \emph{Proceedings of the IEEE Symposium on
        Large-Scale Data Anaysis and Visualization}, pages 91--95, October
      2012. DOI~10.1109/LDAV.2012.6378981.
    \item[An Image Compositing Solution at Scale.] Kenneth Moreland, Wesley
      Kendall, Tom Peterka, and Jian Huang. In \emph{Proceedings of 2011
        International Conference for High Performance Computing,
        Networking, Storage and Analysis (SC '11)}. November
      2011. DOI~10.1145/2063384.2063417.
    \item[Examples of \emph{In Transit} Visualization.] Kenneth Moreland,
      Ron Oldfield, Pat Marion, Sebastien Jourdain, Norbert Podhorszki,
      Venkatram Vishwanath, Nathan Fabian, Ciprian Docan, Manish Parashar,
      Mark Hereld, Michael E. Papka, and Scott Klasky. In \emph{Petascale
        Data Analytics: Challenges and Opportunities (PDAC-11)}, November
      2011. DOI~10.1145/2110205.2110207.
    \item[Dax Toolkit: A Proposed Framework for Data Analysis and
      Visualization at] Extreme Scale. Kenneth Moreland, Utkarsh Ayachit,
      Berk Geveci, and Kwan-Liu Ma. In \emph{IEEE Symposium on Large-Scale
        Data Analysis and Visualization (LDAV)}, pp. 97--104, October
      2011. DOI~10.1109/LDAV.2011.6092323.
    \item[The ParaView Coprocessing Library: A Scalable, General Purpose
      \emph{In Situ}] Visualization Library. Nathan Fabian, Kenneth
      Moreland, David Thompson, Andrew C. Bauer, Pat Marion, Berk Geveci,
      Michel Rasquin, and Kenneth E. Jansen. In \emph{IEEE Symposium on
        Large-Scale Data Analysis and Visualization (LDAV)}, pages 89--96,
      October 2011. DOI~10.1109/LDAV.2011.6092322.
    \item[IceT Users' Guide and Reference.] Kenneth Moreland. \emph{Tech
      Report} SAND 2011-5011, Sandia National Laboratories, August 2011.
    \item[In Situ Data Processing for Extreme Scale Computing.] Scott
      Klasky, et al. In \emph{Proceedings of SciDAC 2011}, July 2011.
    \item[Scientific Discovery at the Exascale: Report from the DOE ASCR
      2011] Workshop on Exascale Data Management, Analysis, and
      Visualization. Sean Ahern, et al. February 2011.
    \item[Visualization on Supercomputing Platform Level II ASC Milestone]
      (3537-1B) Results from Sandia. Kenneth Moreland, Nathan Fabian, Pat
      Marion, and Berk Geveci. \emph{Tech Report} SAND 2010-6118, Sandia
      National Laboratories, September 2010.
    \item[Diverging Color Maps for Scientific Visualization.] Kenneth
      Moreland. In \emph{Proceedings of the 5th International Symposium on
        Visual Computing}, December 2009. DOI~10.1007/978-3-642-10520-3\_9.
    \item[Scalable Analysis Tools for Sensitivity Analysis and UQ (3160)
      Results.] Lisa Ice, Nathan Fabian, Kenneth D Moreland, Janine
      C. Bennett, David C. Thompson, David B. Karelitz, and W. Alan
      Scott. \emph{Tech Report} SAND 2009-6032, Sandia National
      Laboratories, September 2009.
    \item[Next-Generation Visualization Technologies: Enabling Discoveries
      at]~\\ Extreme Scale. Kwan-Liu Ma, Chaoli Wang, Hongfeng Yu, Kenneth
      Moreland, Jian Huang, and Rob Ross. \emph{SciDAC Review}. Issue 12,
      pages 12--21, Spring 2009.
    \item[Design Issues for Performing In Situ Analysis of Simulation
      Data.] David Thompson, Nathan D. Fabian, Kenneth D. Moreland, and
      Lisa G. Ice. \emph{Tech Report} SAND 2009-2014, Sandia National
      Laboratories, April 2009.
    \item[Analysis of Fragmentation in Shock Physics Simulation.] Kenneth
      Moreland, C. Charles Law, Lisa Ice, and David Karelitz. In
      \emph{Proceedings of the 2008 Workshop on Ultrascale Visualization},
      pages 40--46, November 2008. DOI~10.1109/ULTRAVIS.2008.5154062.
    \item[Visualization and parallel I/O at extreme scale.] R~B~Ross,
      T~Peterka, H-W~Shen, Y~Hong, K-L~Ma, H~Yu, and
      K~Moreland. \emph{Journal of Physics: Conference Series}, Volume 125,
      Number 012099, 2008. DOI~10.1088/1742-6596/125/1/012099.
    \item[Post-Processing V\&V Level II ASC Milestone (2843) Results.] David
      B. Karelitz, Lisa Ice, Jason Wilke, Stephen W. Attaway, and Kenneth
      Moreland. \emph{Tech Report} SAND 2008-6183, Sandia National
      Laboratories, September 2008.
    \item[Large Scale Visualization on the Cray XT3 Using ParaView.]
      Kenneth Moreland, David Rogers, John Greenfield, Berk Geveci, Patrick
      Marion, Alexander Neundorf, and Kent Eschenberg. In \emph{Cray User
        Group 2008}.
    \item[Time Dependent Processing in a Parallel Pipeline Architecture.]
      John Biddiscombe, Berk Geveci, Ken Martin, Kenneth Moreland, and
      David Thompson.  \emph{IEEE Transactions on Visualization and
        Computer Graphics}, Volume 12, Number 6, pages 1376--1383,
      November/December 2007.  DOI~10.1109/TVCG.2007.70600.
    \item[Intelligence Analysis Using Titan.] Patricia Crossno, Brian
      Wylie, Andrew Wilson, John Greenfield, Eric Stanton, Timothy Shead,
      Lisa Ice, Kenneth Moreland, Jeffrey Baumes, Berk Geveci. In
      \emph{IEEE Symposium on Visual Analytics Science and Technology
        2007}. October 2007.
    \item[Ultra-Scale Visualization: Research and Education.] Kwan-Liu Ma,
      Robert Ross, Jian Huang, Greg Humphreys, Nelson Max, Kenneth
      Moreland, John D. Owens, and Han-Wei Shen. \emph{Journal of Physics:
        Conference Series}, Volume 78, Number 012088,
      2007. DOI~10.1088/1742-6596/78/1/012088.
    \item[Massive Graph Visualization: LDRD Final Report.] Kenneth Moreland
      and Brian Wylie.  \emph{Tech Report} SAND 2007-6307, October 2007.
    \item[Post-Processing V\&V Level II ASC Milestone (2360) Results.]
      David B. Karelitz, Elmer (Alfonso) Chavez, V. Gregory Weirs, Timothy
      M. Shead, Kenneth D. Moreland, Thomas A. Brunner, and Timothy
      G. Trucano.  \emph{Tech Report} SAND 2007-6006, September 2007.
    \item[Parallel Unstructured Volume Rendering in ParaView.] Kenneth
      Moreland, Lisa Avila, and Lee Ann Fisk.  In \emph{Visualization and
        Data Analysis 2007, Proceedings of SPIE-IS\&T Electronic Imaging},
      pages 64950F-1--12, January 2007.
    \item[Using Ghost Cells in Parallel Filters.] Kenneth Moreland.
      \emph{Kitware Source}, Issue 1, pages 3--4, July 2006.
    \item[Remote Large Data Visualization in the ParaView Framework.] Andy
      Cedilnik, Berk Geveci, Kenneth Moreland, James Ahrens, and Jean
      Favre.  In \emph{Eurographics Parallel Graphics and Visualization
        2006}, pages 163--170, May 2006.
    \item[The ParaView Guide.] Amy Henderson Squillacote.  Kitware
      Inc., ISBN~1-930934-17-3, 2006. (contributed chapters)
    \item[A Fast High Accuracy Volume Renderer for Unstructured Data.]
      Kenneth Moreland and Edward Angel.  In \emph{Proceedings of the
        IEEE/SIGGRAPH Symposium on Volume Visualization}, pages 9--16,
      October 2004.
    \item[Fast High Accuracy Volume Rendering.] Kenneth Moreland.  PhD
      thesis, University of New Mexico, July 2004.
    \item Kenneth Moreland and David Thompson.  ``From Cluster to Wall
      with VTK.''  In \emph{Proceedings of IEEE 2003 Symposium on
      Parallel and Large-Data Visualization and Graphics}, pages 25--31,
      October 2003.
    \item[The FFT on a GPU.] Kenneth Moreland and Edward Angel.  In
      \emph{Proceedings of SIGGRAPH/Eurographics Workshop on Graphics
        Hardware 2003}, pages 112--119, July 2003.
    \item[Tetrahedral Projection using Vertex Shaders.] Brian Wylie,
      Kenneth Moreland, Lee Ann Fisk, and Patricia Crossno.  In
      \emph{Proceedings of the IEEE Symposium on Volume Visualization and
        Graphics 2002}, pages 7--12, October 2002.
    \item[Sort-Last Parallel Rendering for Viewing Extremely Large Data
      Sets on]~\\ Tile Displays. Kenneth Moreland, Brian Wylie, and
      Constantine Pavlakos.  In \emph{Proceedings of the IEEE Symposium on
        Parallel and Large-Data Visualization and Graphics}, pages 85--92,
      October 2001.
    \item[Scalable Rendering on PC Clusters.] Brian Wylie, Constantine
      Pavlakos, Vasily Lewis, and Kenneth Moreland.  \emph{IEEE Computer
        Graphics and Applications}, volume 21, number 4, pages 62--70,
      July/August 2001.
    \end{cvlist}

    \begin{cvlist}{Presentations}
    \item[What's New in ParaView.]
      Kenneth Moreland.
      \emph{DOE Computer Graphics Forum}, April 28, 2020.
    \item[VTK-m Update.]
      Kenneth Moreland.
      \emph{DOE Computer Graphics Forum}, April 28, 2020.
    \item[In Situ Visualization and Analysis with Ascent: Using VTK-m.]
      Kenneth Moreland.
      \emph{ECP Annual Meeting} Tutorial, February 4, 2020.
    \item[VTK-m -- A ToolKit for Scientific Visualization on Many-Core Processors.]
      Hank Childs, Kenneth Moreland, David Pugmire, Robert Maynard.
      \emph{IEEE VIS} Tutorial, October 2019.
    \item[Vis Capabilities at Sandia.]
      Kenneth Moreland.
      Informal Review for 1540 Production Codes, June 10, 2019
    \item[What's New in ParaView.]
      Kenneth Moreland.
      \emph{DOE Computer Graphics Forum}, April 23, 2019.
    \item[VTK-m Update.]
      Kenneth Moreland.
      \emph{DOE Computer Graphics Forum}, April 23, 2019.
    \item[In Situ Visualization and Analysis with Ascent: Using VTK-m.]
      Kenneth Moreland.
      ECP Annual Meeting Tutorial, January 17, 2019.
    \item[Building Better Plots.]
      Kenneth Moreland.
      CCR Summer Seminar Talk, July 2018.
    \item[A Brief History of Interactive Visualization.]
      Kenneth Moreland.
      University of Stuttgart Colloquium, June 29, 2018.
    \item[Preparations for Exascale Visualization at DOE.]
      Kenneth Moreland.
      \emph{ISC High Performance}, June 25, 2018.
    \item[The Crazy Future of Vis.]
      Kenneth Moreland, \emph{DOE Computer Graphics Forum}, Panel: 10-year Prognostication and How Do We Get There?, April 25, 2018.
    \item[What's New in ParaView.]
      Kenneth Moreland, \emph{DOE Computer Graphics Forum}, April 24, 2018.
    \item[VTK-m Update.]
      Kenneth Moreland, \emph{DOE Computer Graphics Forum}, April 24, 2018.
    \item[VTK-m: Visualization on Modern Processors.]
      Kenneth Moreland, Kitware Booth, \emph{SC17}, November 15, 2017.
    \item[Large Scale Visualization with ParaView.]
      Kenneth Moreland, W. Alan Scott, David E. DeMarle, Joe Insley, John Patchett, and Jon Woodring.
      Tutorial \emph{Supercomputing 2017}, November 14, 2017.
    \item[Why You Don't Want to do In Situ Visualization, and Why You Have To.]
      Kenneth Moreland, \emph{Computational Science Seminar Series}, Sandia National Laboratories, October 31, 2017.
    \item[High Performance Visualization in the Many-Core Era.]
      Kenneth Moreland, \emph{Computing@PNNL Seminar}, August 2017.
    \item[Why You Don't Want to do In Situ Visualization, and Why You Have To.]
      Kenneth Moreland.
      \emph{ISC Workshop on In Situ Visualization}, June 2017.
    \item[The Many Faces and Solutions of In Situ Visualization.]
      Kenneth Moreland.
      \emph{ISC Workshop on Visualization at Scale}, June 2017.
    \item[Making Better Plots.]
      Kenneth Moreland.
      Sandia Post-Doc Workshop, February 20, 2017.
    \item[VTK-m: Building a Visualization Toolkit for Massively Threaded]~\\ Architectures.
      Kenneth Moreland.
      \emph{Ultrascale Visualization Workshop}, November 17, 2015.
    \item[Large Scale Visualization with ParaView.] Kenneth Moreland, W.
      Alan Scott. Tutorial \emph{International Conference on Supercomputing
        (ICS)}, November 2015.
    \item[Large Scale Visualization with ParaView.] Kenneth Moreland, W.
      Alan Scott, Sabastien Jourdain, David DeMarle, Robert Maynard, Li-Ta
      Lo, and Joseph Insley. Tutorial \emph{Supercomputing 2014}, November
      2014.
    \item[Dax: A Massively Threaded Visualization and Analysis Toolkit for
      Extreme] Scale. \emph{GPU Technology Conference}. March 2014.
    \item[Approaching Production In Situ Visualization for Extreme Scale
      Analysis.] \emph{$16^{\mathrm{th}}$ SIAM Conference on Parallel
      Processing for Scientific Computing}. February 2014.
    \item[15 Years of Large-Scale Scientific Visualization.] University of
      Oregon colloquium. January 2014.
    \item[Large Scale Visualization with ParaView.] Kenneth Moreland, W.
      Alan Scott, David DeMarle, and Li-Ta Lo. Tutorial
      \emph{Supercomputing 2013}, November 2013.
    \item[Large Scale Visualization with ParaView.] Kenneth Moreland,
      W. Alan Scott, Nathan Fabian, Utkarsh Ayachit, and Robert
      Maynard. Tutorial \emph{Supercomputing 2012}, November 2012.
    \item[Next-Generation Capabilities for Large-Scale Scientific
      Visualization.] Kenneth Moreland, Nathan Fabian, Berk Geveci, Utkarsh
      Ayachit, and James Ahrens. \emph{Massively Parallel, Scalable
        Algorithms and Softwares for Scientific Applications, 15th SIAM
        Conference on Parallel Processing for Scientific Computing},
      February 2012.
    \item[Flexible In Situ with ParaView.] Kenneth Moreland, Nathan Fabian,
      Scott Klasky, and Berk Geveci. \emph{2011 Workshop on Ultrascale
        Visualization}, November 2011.
    \item[Large Scale Visualization with ParaView.] Kenneth Moreland,
      W. Alan Scott, Nathan Fabian, Jeffrey Mauldin, Andrew C. Bauer,
      Robert Maynard, and Scott Klasky. Tutorial \emph{Supercomputing
        2011}, November 2011.
    \item[Large-Scale Interactive Visualization with ParaView.] Kenneth
      Moreland. \emph{2nd International Conference on Computational
        Engineering}, October 2011.
    \item[Large Scale Visualization with ParaView.] Kenneth
      Moreland. Tutorial \emph{SciDAC 2011}, July 2011.
    \item[In-Situ Visualization with the ParaView Coprocessing Library.]
      Kenneth Moreland, Andrew Bauer, Pat Marion, and Nathan
      Fabian. Tutorial \emph{Supercomputing 2010}, November 2010.
    \item[Large Scale Visualization with ParaView.] Kenneth Moreland,
      Andrew Bauer. Tutorial \emph{SciDAC 2010}, July 2010.
    \item[Large Scale Visualization with ParaView.] Kenneth Moreland, John
      Greenfield, W. Alan Scott, Utkarsh Ayachit, and Berk Geveci. Tutorial
      \emph{Supercomputing 2009}, November 2009.
    \item[Parallel Distributed-Memory Visualization with ParaView.] Kenenth
      Moreland and David DeMarle. Tutorial \emph{IEEE Cluster 2009}, August
      2009.
    \item[Large Scale Visualization with ParaView.] Kenneth Moreland, John
      Greenfield, W. Alan Scott, Utkarsh Ayachit, Berk Geveci, and David
      DeMarle. Tutorial \emph{Supercomputing 2008}, November 2008.
    \item[Advanced ParaView Visualization.] Kenneth Moreland, Utkarsh
      Ayachit, Timothy Shead, John Biddiscombe, and David
      Thompson. Tutorial \emph{IEEE Visualization 2008}, October 2008.
    \item[Large Scale Visualization with ParaView 3.] Kenneth Moreland and
      John Greenfield. Tutorial Supercomputing 2007, November 2007.
    \item[Parallel Visualization with ParaView.] Kenneth Moreland and Berk
      Geveci. Tutorial \emph{Supercomputing 2005}, November 2005.
    \item[Large Scale Visualization with Cluster Computing.] Kenneth
      Moreland. \emph{Linux Cluster Institute Workshop}, October 2004.
    \item[Big Data, Big Displays, and Cluster-Driven Interactive
      Visualization.] Kenneth Moreland. Colloquium, University of New
      Mexico, November 2002.
    \item[Big Data, Big Displays, and Cluster-Driven Interactive
      Visualization.] Kenneth Moreland. \emph{Workshop on Commodity-Based
      Visualization Clusters}, October 2002.
    \end{cvlist}

    \begin{cvlist}{Panels}
    \item[How Ubiquitous Parallel Devices Affect Visualization.]
      \emph{Eurographics Symposium on Parallel Graphics and Visualization (EGPGV)}, 2020
    \item[Color Mapping in Vis: Perspectives on Optimal Solutions.]
      \emph{IEEE Visualization}, October 2015.
    \end{cvlist}

    \begin{cvlist}{Professional Activities}
    \item[Institute of Electrical and Electronic Engineers (IEEE)]
      Member since 1995.
    \item[Association for Computing Machinery (ACM)]  Member since 1998.
    \item[Steering Committee Member]~\\
      \begin{itemize}
      \item
        IEEE Symposium on Large Data Analysis and Visualization (LDAV): 2020.
      \item
        International Symposium on Visual Computing (ISVC): 2020.
      \end{itemize}
    \item[Event Chair/Co-Chair]~\\
      \begin{itemize}
      \item
        IEEE Symposium on Large Data Analysis and Visualization (LDAV): 2018, 2019.
      \item
        In Situ Infrastructures for Enabling Extreme-scale Analysis and Visualization (ISAV): 2019.
      \item
        Scientific Visualization \& Data Analytics Showcase, Supercomputing: 2018.
      \item
        VisLies: 2013, 2015, 2016, 2017, 2018, 2019.
      \end{itemize}
    \item[Program Chair/Co-Chair]~\\
      \begin{itemize}
      \item
        In Situ Infrastructures for Enabling Extreme-scale Analysis and Visualization (ISAV): 2017, 2018.
      \item
        IEEE Symposium on Large Data Analysis and Visualization (LDAV): 2016, 2017.
      \item
        Eurographics Symposium on Parallel Graphics and Visualization (EGPGV): 2013.
      \end{itemize}
    \item[Program Committee Member]~\\
      \begin{itemize}
      \item
        IEEE Scientific Visualization: 2014, 2015, 2016, 2017, 2019, 2020.
      \item
        International Symposium on Visual Computing (ISVC): 2013, 2014, 2019, 2020.
      \item
        Eurographics Symposium on Parallel Graphics and Visualization (EGPGV): 2009, 2010, 2011, 2012, 2013, 2015, 2016, 2017, 2019, 2020.
      \item
        VisGap: 2020.
      \item
        EuroVis: 2016, 2017, 2018.
      \item
        Symposium on Visualization: 2017.
      \item
        Scientific Visualization \& Data Analytics Showcase, Supercomputing: 2017.
      \item
        IEEE Cluster: 2015, 2016.
      \item
        Visualization in High Performance Computing: 2015.
      \item
        Large Data Analysis and Visualization (LDAV): 2011, 2013, 2014.
      \item
        Ultrascale Visualization: 2013, 2014.
      \item
        International Conference for High Performance Computing, Networking, Storage, and Analysis (Supercomputing): 2012, 2013.
      \item
        Big Data Analytics: Challenges and Opportunities: 2012, 2013.
      \item
        Visualization Infrastructure \& Systems Technology: 2014.
      \end{itemize}
    \item[Review Panels]~\\
      \begin{itemize}
      \item
        NSF IIS Division: 2012, 2014, 2015, 2016, 2018.
      \item
        DOE SBIR Phase II: 2012, 2014.
      \item
        DOE ECRP: 2009, 2013.
      \item
        DOE ASCR: 2009, 2010, 2011, 2013.
      \item
        DOE SBIR Phase I: 2010, 2011.
      \end{itemize}
    \item[Miscellaneous]~\\
      \begin{itemize}
      \item
        Guest Editor, \emph{Parallel Computing}: 2019.
      \item
        VIS Doctoral Colloquium Panelist: 2017.
      \end{itemize}
    \end{cvlist}

  \end{cv}

\end{document}
