\begin{enumerate}[label={[\arabic*]}, left=0pt]
\item  % Wang2025:participation
  Zhe Wang, \textbf{Kenneth Moreland}, Matthew Larsen, James Kress, Hank Childs, and David Pugmire.
  Parallelize Over Data Particle Advection: Participation, Ping Pong Particles, and Overhead.
  \emph{IEEE Transactions on Visualization and Computer Graphics}, 10, 31(10):7795--7808, October 2025.
  doi:10.1109/TVCG.2025.3557453.
\item  % Ahrens2025
  James Ahrens, Hank Childs, and \textbf{Kenneth Moreland}.
  The Origins of the ParaView and VisIt Scientific Visualization Tools.
  \emph{IEEE Computer Graphics and Applications}, 5, 45(5):127--137, September 2025.
  doi:10.1109/MCG.2025.3595349.
\item  % Wang2025:assignment
  Zhe Wang, \textbf{Kenneth Moreland}, Matthew Larsen, James Kress, Hank Childs, Guan Li, Guihua Shan, and David Pugmire.
  {\it In Situ} Workload Estimation for Block Assignment and Duplication in Parallelization-Over-Data Particle Advection.
  \emph{Computer Graphics Forum}, 3, 44(3), May 2025.
  doi:10.1111/cgf.70108.
\item  % Athawale2025
  Tushar M. Athawale, Zhe Wang, David Pugmire, \textbf{Kenneth Moreland}, Qian Gong, Scott Klasky, Chris R. Johnson, and Paul Rosen.
  Uncertainty Visualization of Critical Points of {2D} Scalar Fields for Parametric and Nonparametric Probabilistic Models.
  \emph{IEEE Transactions on Visualization and Computer Graphics}, 1, 31(1):108--118, January 2025.
  doi:10.1109/TVCG.2024.3456393.
\item  % Moreland2024:IJHPCA
  \textbf{Kenneth Moreland}, Tushar M. Athawale, Vicente Bolea, Mark Bolstad, Eric Brugger, Hank Childs, Axel Huebl, Li-Ta Lo, Berk Geveci, Nicole Marsaglia, Sujin Philip, David Pugmire, Silvio Rizzi, Zhe Wang, and Abhishek Yenpure.
  {Visualization at exascale: Making it all work with VTK-m}.
  \emph{The International Journal of High Performance Computing Applications}, 5, 38(5):508--526, August 2024.
  doi:10.1177/10943420241270969.
\item  % Samsel2024
  Francesca Samsel, W. Alan Scott, and \textbf{Kenneth Moreland}.
  A New Default Colormap for {ParaView}.
  \emph{IEEE Computer Graphics and Applications}, 4, 44(4):150--160, July 2024.
  doi:10.1109/MCG.2024.3383137.
\item  % Moreland2021
  \textbf{Kenneth Moreland}, Robert Maynard, David Pugmire, Abhishek Yenpure, Allison Vacanti, Matthew Larsen, and Hank Childs.
  Minimizing Development Costs for Efficient Many-Core Visualization Using {MCD$^3$}.
  \emph{Parallel Computing}, 102834, 108(102834), December 2021.
  doi:10.1016/j.parco.2021.102834.
\item  % Moreland2020:SIAM
  \textbf{Kenneth Moreland} and Hank Childs.
  Scientific Visualization: New Techniques in Production Software.
  \emph{SIAM News}, November 2020.
\item  % Childs2020
  Hank Childs, \emph{et al}.
  A terminology for in situ visualization and analysis systems.
  \emph{The International Journal of High Performance Computing Applications}, August 2020.
  doi:10.1177/1094342020935991.
\item  % Choi2018
  J. Y. Choi, C. Chang, J. Dominski, S. Klasky, G. Merlo, E. Suchyta, M. Ainsworth, B. Allen, F. Cappello, M. Churchill, P. Davis, S. Di, G. Eisenhauer, S. Ethier, I. Foster, B. Geveci, H. Guo, K. Huck, F. Jenko, M. Kim, J. Kress, S. Ku, Q. Liu, J. Logan, A. Malony, K. Mehta, \textbf{K. Moreland}, T. Munson, M. Parashar, T. Peterka, N. Podhorszki, D. Pugmire, O. Tugluk, R. Wang, B. Whitney, M. Wolf, and C. Wood.
  Coupling Exascale Multiphysics Applications: Methods and Lessons Learned.
  In \emph{2018 IEEE 14th International Conference on e-Science (e-Science)}, pages 442--452, October 2018.
  doi:10.1109/eScience.2018.00133.
\item  % Deelman2018
  Ewa Deelman, Tom Peterka, Ilkay Altintas, Christopher D Carothers, Kerstin Kleese van Dam, \textbf{Kenneth Moreland}, Manish Parashar, Lavanya Ramakrishnan, Michela Taufer, and Jeffrey Vetter.
  The future of scientific workflows.
  \emph{International Journal of High Performance Computing Applications}, 1, 32(1):159--175, January 2018.
  doi:10.1177/1094342017704893.
\item  % Bauer2016
  Andrew C. Bauer, Hasan Abbasi, James Ahrens, Hank Childs, Berk Geveci, Scott Klasky, \textbf{Kenneth Moreland}, Patrick O'Leary, Venkatram Vishwanath, Brad Whitlock, and E. Wes Bethel.
  In Situ Methods, Infrastructures, and Applications on High Performance Computing Platforms.
  \emph{Computer Graphics Forum}, 3, 35(3):577--597, June 2016.
  doi:10.1111/cgf.12930.
\item  % Moreland2016:VTKm
  \textbf{Kenneth Moreland}, Christopher Sewell, William Usher, Li-Ta Lo, Jeremy Meredith, David Pugmire, James Kress, Hendrik Schroots, Kwan-Liu Ma, Hank Childs, Matthew Larsen, Chun-Ming Chen, Robert Maynard, and Berk Geveci.
  {VTK-m}: Accelerating the Visualization Toolkit for Massively Threaded Architectures.
  \emph{IEEE Computer Graphics and Applications}, 3, 36(3):48--58, May/June 2016.
  doi:10.1109/MCG.2016.48.
\item  % Moreland2016:VisView
  \textbf{Kenneth Moreland}.
  The Tensions of In Situ Visualization.
  \emph{IEEE Computer Graphics and Applications}, 2, 36(2):5--9, March/April 2016.
  doi:10.1109/MCG.2016.35.
\item  % Moreland2015:ISC
  \textbf{Kenneth Moreland} and Ron Oldfield.
  Formal Metrics for Large-Scale Parallel Performance.
  In \emph{ISC High Performance}, pages 488--496, June 2015.
  doi:10.1007/978-3-319-20119-1\_34.
\item  % Oldfield2014
  Ron A. Oldfield, \textbf{Kenneth Moreland}, Nathan Fabian, and David Rogers.
  Evaluation of Methods to Integrate Analysis into a Large-Scale Shock Physics Code.
  In \emph{Proceedings of the 28th ACM international Conference on Supercomputing (ICS '14)}, pages 83--92, June 2014.
  doi:10.1145/2597652.2597668.
\item  % Tchoua2013
  Roselyne Tchoua, Jong Choi, Scott Klasky, Qing Liu, Jeremy Logan, \textbf{Kenneth Moreland}, Jingqing Mu, Manish Parashar, Norbert Podhorszki, David Pugmire, and Matthew Wolf.
  {ADIOS} Visualization Schema: A First Step Towards Improving Interdisciplinary Collaboration in High Performance Computing.
  In \emph{IEEE International Conference on eScience}, pages 27--34, October 2013.
  doi:10.1109/eScience.2013.24.
\item  % Childs2013
  Hank Childs, Berk Geveci, Will Schroeder, Jeremy Meredith, \textbf{Kenneth Moreland}, Christopher Sewell, Torsten Kuhlen, and E. Wes Bethel.
  Research Challenges for Visualization Software.
  \emph{IEEE Computer}, 5, 46(5):34--42, May 2013.
  doi:10.1109/MC.2013.179.
\item  % Moreland2013:TVCG
  \textbf{Kenneth Moreland}.
  A Survey of Visualization Pipelines.
  \emph{IEEE Transactions on Visualization and Computer Graphics}, 3, 19(3):367--378, March 2013.
  doi:10.1109/TVCG.2012.133.
\item  % Moreland2011:SC
  \textbf{Kenneth Moreland}, Wesley Kendall, Tom Peterka, and Jian Huang.
  An Image Compositing Solution at Scale.
  In \emph{Proceedings of 2011 International Conference for High Performance Computing, Networking, Storage and Analysis (SC '11)}, November 2011.
  doi:10.1145/2063384.2063417.
\item  % Biddiscombe2007
  John Biddiscombe, Berk Geveci, Ken Martin, \textbf{Kenneth Moreland}, and David Thompson.
  Time Dependent Processing in a Parallel Pipeline Architecture.
  \emph{IEEE Transactions on Visualization and Computer Graphics}, 6, 13(6):1376--1383, November/December 2007.
  doi:10.1109/TVCG.2007.70600.
\item  % Wylie2001
  Brian Wylie, Constantine Pavlakos, Vasily Lewis, and \textbf{Kenneth Moreland}.
  Scalable Rendering on {PC} Clusters.
  \emph{IEEE Computer Graphics and Applications}, 4, 21(4):62--70, July/August 2001.
\end{enumerate}