\begin{enumerate}[label={[\arabic*]}, left=0pt]
\item  % Duggan2025:poster
  John Duggan, Dave Pugmire, \textbf{Ken Moreland}, Greg Watson, Sergey Yakubov, Greg Cage, and Andrew Ayres.
  Visualizing Imaging Data with {NDIP} and {NOVA}.
  In \emph{Joint Nanoscience and Neutron Scattering User Meeting}, August 2025.
\item  % Yakubov2025:Poster
  Sergey Yakubov, Greg Watson, Greg Cage, John Duggan, Andrew Ayres, Dave Pugmire, \textbf{Ken Moreland}, Kristin Maroun, and Randall Petras.
  {NDIP} and {NOVA}: Workflows and Interfaces for Neutron Scattering.
  In \emph{Joint Nanoscience and Neutron Scattering User Meeting}, August 2025.
\item  % Maynard2013:poster
  Robert Maynard, \textbf{Kenneth Moreland}, Utkarsh Ayachit, Berk Geveci, and Kwan-Liu Ma.
  Optimizing Threshold for Extreme Scale Analysis.
  In \emph{Proceedings of SPIE Visualization and Data Analysis}, 2013.
\item  % Moreland2011:poster
  \textbf{Kenneth Moreland}, Utkarsh Ayachit, Berk Geveci, and Kwan-Liu Ma.
  Dax: Data Analysis at Extreme.
  In \emph{Proceedings of SciDAC}, July 2011.
\item  % Peterka2010:poster
  T Peterka, W Kendall, D Goodell, B Nouanesengsey, H-W Shen, J Huang, \textbf{K Moreland}, R Thakur, and R B Ross.
  Performance of communication patterns for extreme-scale analysis and visualization.
  In \emph{Proceedings of SciDAC}, 2010.
\item  % Moreland2008:poster
  \textbf{Kenneth Moreland}, Daniel Lepage, David Koller, and Greg Humphreys.
  Remote rendering for ultrascale data.
  \emph{Journal of Physics: Conference Series}, 012096, 125(012096), 2008.
\end{enumerate}