\begin{enumerate}[label={[\arabic*]}, left=0pt]
\item  % Hari2024
  Gautam Hari, Nrushad Joshi, Zhe Wang, Qian Gong, Dave Pugmire, \textbf{Kenneth Moreland}, Chris R. Johnson, Scott Klasky, Norbert Podhorszki, and Tushar M. Athawale.
  {FunM$^2$C}: A Filter for Uncertainty Visualization of Multivariate Data on Multi-Core Devices.
  In \emph{Proceedings IEEE Workshop on Uncertainty Visualization}, pages 43--47, October 2024.
  doi:10.1109/UncertaintyVisualization63963.2024.00010.
\item  % Sisneros2024
  Robert Sisneros, Tushar Athawale, David Pugmire, and \textbf{Kenneth Moreland}.
  An Entropy-Based Test and Development Framework for Uncertainty Modeling in Level-Set Visualizations.
  In \emph{Proceedings IEEE Workshop on Uncertainty Visualization}, pages 78--83, October 2024.
  doi:10.1109/UncertaintyVisualization63963.2024.00015.
\item  % Hammer2024
  James Hammer, Tanner Hobson, David Pugmire, Scott Klasky, \textbf{Kenneth Moreland}, and Jian Huang.
  A Personalized {AI} Assistant For Intuition-Driven Visual Explorations.
  In \emph{IEEE 20th International Conference on e-Science (e-Science)}, September 2024.
  doi:10.1109/e-Science62913.2024.10678681.
\item  % Pugmire2024b
  David Pugmire, \textbf{Kenneth Moreland}, Tushar M. Athawale, James Hammer, and Jian Huang.
  Top Research Challenges and Opportunities for Near Real-Time Extreme-Scale Visualization of Scientific Data.
  In \emph{Proceedings IEEE 20th International Conference on e-Science}, September 2024.
  doi:10.1109/e-Science62913.2024.10678727.
\item  % Pugmire2024a
  David Pugmire, Jong Y. Choi, Scott Klasky, \textbf{Kenneth Moreland}, Eric Suchyta, Tushar M. Athawale, Zhe Wang, Choong-Seock Chang, Seung-Hoe Ku, and Robert Hager.
  Performance Improvements of {Poincar\'{e}} Analysis for Exascale Fusion Simulations.
  In \emph{VisGap - The Gap between Visualization Research and Visualization Software}, May 2024.
  doi:10.2312/visgap.20241120.
\item  % Tsalikis2024
  Spiros Tsalikis, Will Schroeder, Daniel Szafir, and \textbf{Kenneth Moreland}.
  An Accelerated Clip Algorithm for Unstructured Meshes: A Batch-Driven Approach.
  In \emph{Eurographics Symposium on Parallel Graphics and Visualization (EGPGV)}, May 2024.
  doi:10.2312/pgv.20241130.
\item  % Wang2023
  Zhe Wang, Tushar M. Athawale, \textbf{Kenneth Moreland}, Jieyang Chen, Chris R. Johnson, and David Pugmire.
  {FunMC$^2$}: A Filter for Uncertainty Visualization of Marching Cubes on Multi-Core Devices.
  In \emph{Eurographics Symposium on Parallel Graphics and Visualization (EGPGV)}, May 2023.
  doi:10.2312/pgv.20231081.
\item  % Moreland2022:InSitu
  \textbf{Kenneth Moreland}, Andrew C. Bauer, Berk Geveci, Patrick O'Leary, and Brad Whitlock.
  Leveraging Production Visualization Tools In Situ.
  In \emph{In Situ Visualization for Computational Science}, Springer, pages 205--231, 2022.
  doi:10.1007/978-3-030-81627-8\_10.
  ISBN:978-3-030-81626-1.
\item  % Ayachit2021
  Utkarsh Ayachit, Andrew C. Bauer, Ben Boeckel, Berk Geveci, \textbf{Kenneth Moreland}, Patrick O'Leary, and Tom Osika.
  Catalyst Revised: Rethinking the ParaView in Situ Analysis and Visualization {API}.
  In \emph{High Performance Computing}, pages 484--494, June 2021.
  doi:10.1007/978-3-030-90539-2\_33.
\item  % Sane2021
  Sudhanshu Sane, Abhishek Yenpure, Roxana Bujack, Matthew Larsen, \textbf{Kenneth Moreland}, Christoph Garth, Chris R. Johnson, and Hank Childs.
  Scalable In Situ Computation of {Lagrangian} Representations via Local Flow Maps.
  In \emph{Eurographics Symposium on Parallel Graphics and Visualization (EGPGV)}, June 2021.
Winner best paper.  doi:10.2312/pgv.20211040.
\item  % Lipinksi2021
  Riley Lipinksi, \textbf{Kenneth Moreland}, Michael E. Papka, and Thomas Marrinan.
  {GPU}-based Image Compression for Efficient Compositing in Distributed Rendering Applications.
  In \emph{2021 IEEE 11th Symposium on Large Data Analysis and Visualization (LDAV)}, pages 43--52, 2021.
  doi:10.1109/LDAV53230.2021.00012.
\item  % Yenpure2019
  Abhishek Yenpure, Hank Childs, and \textbf{Kenneth Moreland}.
  Efficient Point Merging Using Data Parallel Techniques.
  In \emph{Eurographics Symposium on Parallel Graphics and VIsualization (EGPGV)}, June 2019.
  doi:10.2312/pgv.20191112.
\item  % Moreland2018
  \textbf{Kenneth Moreland}.
  Comparing Binary-Swap Algorithms for Odd Factors of Processes.
  In \emph{Proceedings of the 8th IEEE Symposium on Large Data Analysis and Visualization (LDAV)}, October 2018.
  doi:10.1109/LDAV.2018.8739210.
\item  % Lessley2017:Duplicate
  Brenton Lessley, \textbf{Kenneth Moreland}, Matthew Larsen, and Hank Childs.
  Techniques for Data-Parallel Searching for Duplicate Elements.
  In \emph{IEEE Symposium on Large Data Analysis and Visualization (LDAV)}, October 2017.
  doi:10.1109/LDAV.2017.8231845.
\item  % Larsen2016
  Matthew Larsen, \textbf{Kenneth Moreland}, Chris Johnson, and Hank Childs.
  Optimizing Multi-Image Sort-Last Parallel Rendering.
  In \emph{Proceedings of the IEEE Symposium on Large Data Analysis and Visualization (LDAV)}, October 2016.
  doi:10.1109/LDAV.2016.7874308.
\item  % Moreland2016:HVEI
  \textbf{Kenneth Moreland}.
  Why We Use Bad Color Maps and What You Can Do About It.
  In \emph{Proceedings of Human Vision and Electronic Imaging (HVEI)}, February 2016.
  doi:10.2352/ISSN.2470-1173.2016.16.HVEI-133.
\item  % Ayachit2015
  Utkarsh Ayachit, Andrew Bauer, Berk Geveci, Patrick O'Leary, \textbf{Kenneth Moreland}, Nathan Fabian, and Jeffrey Mauldin.
  ParaView Catalyst: Enabling In Situ Data Analysis and Visualization.
  In \emph{Proceedings of the First Workshop on In Situ Infrastructures for Enabling Extreme-Scale Analysis and Visualization (ISAV 2015)}, pages 25--29, November 2015.
  doi:10.1145/2828612.2828624.
\item  % Moreland2015:SFI
  \textbf{Kenneth Moreland}, Matthew Larsen, and Hank Childs.
  Visualization for Exascale: Portable Performance is Critical.
  \emph{Supercomputing Frontiers and Innovations}, 3, 2(3), November 2015.
  doi:10.14529/jsfi150306.
\item  % Miller2014
  Robert Miller, \textbf{Kenneth Moreland}, and Kwan-Liu Ma.
  Finely-Threaded History-Based Topology Computation.
  In \emph{Eurographics Symposium on Parallel Graphics and Visualization}, June 2014.
  doi:10.2312/pgv.20141083.
\item  % Moreland2013:UltraVis
  \textbf{Kenneth Moreland}, Berk Geveci, Kwan-Liu Ma, and Robert Maynard.
  A Classification of Scientific Visualization Algorithms for Massive Threading.
  In \emph{Proceedings of Ultrascale Visualization Workshop}, November 2013.
  doi:10.1145/2535571.2535591.
\item  % Ayachit2013
  Utkarsh Ayachit, Berk Geveci, \textbf{Kenneth Moreland}, John Patchett, and Jim Ahrens.
  The ParaView Visualization Application  \emph{High Performance Visualization: Enabling Extreme Scale Insight}, CRC Press, pages 383--400, 2013.
  ISBN:978-1-4398-7572-8.
\item  % Moreland2013
  \textbf{Kenneth Moreland}.
  IceT  \emph{High Performance Visualization: Enabling Extreme Scale Insight}, CRC Press, pages 373--382, 2013.
  ISBN:978-1-4398-7572-8.
\item  % Moreland2012:PDAC
  \textbf{Kenneth Moreland}, Brad King, Robert Maynard, and Kwan-Liu Ma.
  Flexible Analysis Software for Emerging Architectures.
  In \emph{2012 SC Companion (Petascale Data Analytics: Challenges and Opportunities)}, pages 821--826, November 2012.
  doi:10.1109/SC.Companion.2012.115.
\item  % Moreland2012:LDAV
  \textbf{Kenneth Moreland}.
  Redirecting Research in Large-Format Displays for Visualization.
  In \emph{Proceedings of the IEEE Symposium on Large-Scale Data Analysis and Visualization}, pages 91--95, October 2012.
  doi:10.1109/LDAV.2012.6378981.
\item  % Moreland2011:PDAC
  \textbf{Kenneth Moreland}, Ron Oldfield, Pat Marion, Sebastien Jourdain, Norbert Podhorszki, Venkatram Vishwanath, Nathan Fabian, Ciprian Docan, Manish Parashar, Mark Hereld, Michael E. Papka, and Scott Klasky.
  Examples of {\it In Transit} Visualization.
  In \emph{Petascale Data Analytics: Challenges and Opportunities (PDAC-11)}, November 2011.
\item  % Fabian2011
  Nathan Fabian, \textbf{Kenneth Moreland}, David Thompson, Andrew C. Bauer, Pat Marion, Berk Geveci, Michel Rasquin, and Kenneth E. Jansen.
  The {ParaView} Coprocessing Library: A Scalable, General Purpose In Situ Visualization Library.
  In \emph{Proceedings of the IEEE Symposium on Large-Scale Data Analysis and Visualization}, pages 89--96, October 2011.
  doi:10.1109/LDAV.2011.6092322.
\item  % Moreland2011:LDAV
  \textbf{Kenneth Moreland}, Utkarsh Ayachit, Berk Geveci, and Kwan-Liu Ma.
  Dax Toolkit: A Proposed Framework for Data Analysis and Visualization at Extreme Scale.
  In \emph{Proceedings of the IEEE Symposium on Large-Scale Data Analysis and Visualization}, pages 97--104, October 2011.
  doi:10.1109/LDAV.2011.6092323.
\item  % Klasky2011
  Scott Klasky, \emph{et al}.
  In Situ Data Processing for Extreme Scale Computing.
  In \emph{Proceedings of SciDAC 2011}, July 2011.
\item  % Moreland2009
  \textbf{Kenneth Moreland}.
  Diverging Color Maps for Scientific Visualization.
  In \emph{Advances in Visual Computing (Proceedings of the 5th International Symposium on Visual Computing)}, 5876:92--103, December 2009.
  doi:10.1007/978-3-642-10520-3\_9.
\item  % Ma2009:SciDACReview
  Kwan-Liu Ma, Chaoli Wang, Hongfeng Yu, \textbf{Kenneth Moreland}, Jian Huang, and Rob Ross.
  Next-Generation Visualization Technologies: Enabling Discoveries at Extreme Scale.
  \emph{SciDAC Review}, 12, pages 12--21, Spring 2009.
\item  % Ross2008
  R B Ross, T Peterka, H-W Shen, Y Hong, K-L Ma, H Yu, and \textbf{K Moreland}.
  Visualization and parallel {I/O} at extreme scale.
  \emph{Journal of Physics: Conference Series}, 012099, 125(012099), July 2008.
  doi:10.1088/1742-6596/125/1/012099.
\item  % Ma2007
  Kwan-Liu Ma, Robert Ross, Jian Huang, Greg Humphreys, Nelson Max, \textbf{Kenneth Moreland}, John D. Owens, and Han-Wei Shen.
  Ultra-Scale Visualization: Research and Education.
  \emph{Journal of Physics: Conference Series}, 012088, 78(012088), June 2007.
  doi:10.1088/1742-6596/78/1/012088.
\item  % Moreland2007
  \textbf{Kenneth Moreland}, Lisa Avila, and Lee Ann Fisk.
  Parallel Unstructured Volume Rendering in ParaView.
  In \emph{Visualization and Data Analysis 2007, Proceedings of SPIE-IS\&T Electronic Imaging}, pages 64950F-1--12, January 2007.
\item  % Cedilnik2006
  Andy Cedilnik, Berk Geveci, \textbf{Kenneth Moreland}, James Ahrens, and Jean Farve.
  Remote Large Data Visualization in the {ParaView} Framework.
  In \emph{Eurographics Parallel Graphics and Visualization}, pages 163--170, May 2006.
\item  % Moreland2004:VolVis
  \textbf{Kenneth Moreland} and Edward Angel.
  A Fast High Accuracy Volume Renderer for Unstructured Data.
  In \emph{IEEE Symposium on Volume Visualization and Graphics}, pages 9--16, October 2004.
  doi:10.1109/SVVG.2004.2.
\item  % Moreland2003
  \textbf{Kenneth Moreland} and David Thompson.
  From Cluster to Wall with {VTK}.
  In \emph{Proceedings of IEEE Symposium on Parallel and Large-Data Visualization and Graphics}, pages 25--31, October 2003.
\item  % Moreland2003:FFT
  \textbf{Kenneth Moreland} and Edward Angel.
  {The FFT on a GPU}.
  In \emph{SIGGRAPH/Eurographics Workshop on Graphics Hardware 2003 Proceedings}, pages 112--119, July 2003.
\item  % Wylie2002
  Brian Wylie, \textbf{Kenneth Moreland}, Lee Ann Fisk, and Patricia Crossno.
  Tetrahedral Projection using Vertex Shaders.
  In \emph{Proceedings of IEEE Volume Visualization and Graphics Symposium}, pages 7--12, October 2002.
\item  % Moreland2001
  \textbf{Kenneth Moreland}, Brian Wylie, and Constantine Pavlakos.
  Sort-Last Parallel Rendering for Viewing Extremely Large Data Sets on Tile Displays.
  In \emph{Proceedings of the IEEE 2001 Symposium on Parallel and Large-Data Visualization and Graphics}, pages 85--92, October 2001.
  doi:10.1109/PVGS.2001.964408.
\end{enumerate}